---
title: "introduction"
author: "Roni Shen"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(roller)
```

## Roller

The package `"roller"` implements functions for simulating rolling an object, like a coin or a die, a number of times and the resulting sample and relative frequencies. 



## Creating a `device`

In order to create a `"device"` object with the function `device()`:

```{r}
my_dev <- devive()
my_dev
```

By default, `device()` creates a _fair_ coin with standard sides `1` and 
`2`, and with probability values for each side of 1/2.

You can change the defatuls with arguments `sides` and `prob`:

```{r}
fair_die <- device(
  sides = c('i', 'ii', 'iii', 'iv'), 
  prob = rep(1/4, 4))
fair_die
```



## Rolling a device

Once you have defined a `"device"` object, you can use the function `roll()` to
_roll_ a coin a given number of `times`. The output will be an object of class 
`"roll"`, which will contain the vector of `rolls`:

```{r}
fair50 <- roll(fair_die, times = 50) 
fair50
```

The `summary()` function gives you table of frequencies:
```{r}
summary(fair50)
```



## Plot of relative frequencies

You can use the function `plot()` to create a graohic with the relative 
frequencies of a series of coin tosses:

```{r, fig.show='hold'}
plot(toss100)
```
